Blame and Coercion: Together Again for the Second Time

### 2019-10-16 paper.tex
minor fixes to intro

\citet{siek2012interpretations} present a revised coercion calculi.
\todo[inline]{Actually, Wadler might disagree that the blame calculus is
  a lazy UD calculus... because the blame calculus has polarity in the blame
  labels, and the lazy UD calculus does not. So perhaps we should just
  say lazy UD cast calculus, and explain that it is very close to the
  blame calculus. -Jeremy}
\todo[inline]{I replace most uses of blame calculus to cast calculus.}
They simplify the coercion calculi by only 
working with normal coercions (i.e. coercions in normal form). 
They conjecture that their revised coercion calculi bisimulate the 
corresponding Blame Calculi.

@@

So far, it seems that normal coercion is the best way to combine 
space-efficiency and blame-tracking: normal coercion is claimed easy to 
understand \cite{garcia2013calculating}\cite{siek2015blame} and is shown 
easy enough to implement in a compiler \cite{kuhlenschmidt2018efficient}.
Normal coercion is still not satisfactory, however, in at least two aspects.
Firstly, as we mentioned above, it is hard to reason about normal coercion. The 
major difficulty is from its non-structurally recursive composition.
For instance, many developers of Grift report it is tricky to convince
their proof assistants that the composition terminates.
%
\todo[inline]{Don't lie. There are not many developers of Grift.
  I only know 2 people developing Grift: Andre and Deyaa. -Jeremy}
%
Secondly, the definition of normal coercion lies unnecessarily on top 
of coercion: all coercions are normal when they are initially constructed, and 
\citet{siek2012interpretations} have shown an function that 
composes and produces normal coercions.
%
\todo[inline]{Many researchers would view this as a positive thing,
  not a negative. For example, the notion of normal forms comes up
  over and over again in mathematics and logic. -Jeremy}

@@

The structure of this paper is as follows. 
Section \ref{sec:blame-calculus} reviews the state-of-art of $Lazy$ Blame 
Calculi. 
Section \ref{sec:coercion-calculus} reviews the state-of-art of $Lazy$ Coercion 
Calculi. 
In section \ref{sec:hypercoercion} we present hypercoercion.
Section \ref{sec:conclude} concludes.
\todo[inline]{Lots of missing sections. -Jeremy}

>>>>

\citet{siek2012interpretations} present a revised coercion calculi.
\todo[inline]{Actually, Wadler might disagree that the blame calculus is
  a lazy UD calculus... because the blame calculus has polarity in the blame
  labels, and the lazy UD calculus does not. So perhaps we should just
  say lazy UD cast calculus, and explain that it is very close to the
  blame calculus. -Jeremy}
\todo[inline]{I replace most uses of blame calculus to cast calculus. -KC}
They simplify the coercion calculi by only 
working with normal coercions (i.e. coercions in normal form). 
They conjecture that their revised coercion calculi bisimulate the 
corresponding Blame Calculi.

@@

So far, it seems that normal coercion is the best way to combine 
space-efficiency and blame-tracking: normal coercion is claimed easy to 
understand \cite{garcia2013calculating}\cite{siek2015blame} and is shown 
easy enough to implement in a compiler \cite{kuhlenschmidt2018efficient}.
Normal coercion is still not satisfactory, however, in at least two aspects.
Firstly, as we mentioned above, it is hard to reason about normal coercion. The 
major difficulty is from its non-structurally recursive composition.
For instance, the developers of Grift report it is tricky to convince
their proof assistants that the composition terminates.

Secondly, the definition of normal coercion lies unnecessarily on top 
of coercion: all coercions are normal when they are initially constructed, and 
\citet{siek2012interpretations} have shown an function that 
composes and produces normal coercions.
%
\todo[inline]{Many researchers would view this as a positive thing,
  not a negative. For example, the notion of normal forms comes up
  over and over again in mathematics and logic. -Jeremy}
\todo[inline]{I guess having a notion of normal forms is more convenient when a 
notion of normalization is convenient. But we don't even need a notion of 
normalization for cast representations. -KC}

@@

The structure of this paper is as follows. 
Section \ref{sec:blame-calculus} reviews the state-of-art of $Lazy$ Blame 
Calculi. 
Section \ref{sec:coercion-calculus} reviews the state-of-art of $Lazy$ Coercion 
Calculi. 
In section \ref{sec:hypercoercion} we present hypercoercion.
Section \ref{sec:conclude} concludes.
\todo[inline]{Lots of missing sections. -Jeremy}
\todo[inline]{Will fix finally, I am moving stuff. -KC}
